```{r echo=FALSE}

# Replace with the survey you'd like to report on
SurveyName = "1997 YUCH Moose Survey"

```

---
title: "Moose Survey Database Contents Summary"
author: ""
date: ""
output:
  html_document:
  toc: yes
---

# `r SurveyName`

```{r setup, include=FALSE}

# Setup
options(knitr.kable.NA = '')
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(RODBC)
library(sf)
library(ggplot2)

# Restrain the number of decimal places
options(digits = 1) 

# Database connection string
Connection =  odbcDriverConnect('Driver={SQL Server};Server=inpyugamsvm01\\nuna;Database=Moose;Trusted_connection=yes')

# Function that returns a data frame from an SQL query on the database
# SQL: A valid SQL query
GetDataFrame <- function(SQL) { # create a function with the name my_function
  DF = sqlQuery(Connection,SQL)
  return(DF)
}

# Function to convert a data frame of Lat/Lon pairs to a spatial data frame
# DataFrame: A data frame containing a latitude field and a longitude field
# LatitudeFieldName: The name of the field containing latitude data
# LongitudeFieldName: The name of the field containing longitude data
GetPointSpatialDataFrameFromDataFrame = function(DataFrame,LatitudeFieldName,LongitudeFieldName){
  
  # Convert the data frame into a spatial data frame
  SDF <- sf::st_as_sf(DataFrame, coords = c(LongitudeFieldName,LatitudeFieldName))

  # Set the coordinate system to GCS Lat\Lon WGS1984
  st_crs(SDF) <- st_crs(4326)
  
  return(SDF)
}

# Function that returns an Markdown compatible URL to the IRMA Data Store for the submitted ReferenceCode parameter
GetIRMALinkFromReferenceCode = function(ReferenceCode){
  return(paste("[https://irma.nps.gov/DataStore/Reference/Profile/",ReferenceCode,"](https://irma.nps.gov/DataStore/Reference/Profile/",ReferenceCode,")",sep=""))
}

# Counters to increment the table and figure numbers as the report progresses.
TableCount = 1
FigureCount = 1

```

Scott D. Miller\
Information Technology Specialist/Data Manager\
National Park Service, Arctic Inventory and Monitoring Network\
240 W. 5th Ave.\
Anchorage, AK 99501


```{r label="Dashboard", echo=FALSE}

# Get the summarized data for the comp count survey into a data frame
Sql = paste("SELECT 
SurveyName
, [Year]
, Network
, Park
, Season
, StartDate
, EndDate
, StartMonth
, EndMonth
, AreaSurveyed_mi
, AverageSearchEffort
, Methodology
, ProtocolVersion
, ProtocolReferenceCode
, Personnel
, ReportReferenceCode
, ReportLink
, DeliverablesDatasetReferenceCode
, DataSource
, DataResourcesDirectory
, Abstract
, Summary
, DatasetProcessingSteps
, Comments
FROM GSPE_Surveys
WHERE (SurveyName = '",SurveyName,"')",sep="")

DashboardDF = GetDataFrame(Sql)
Abstract = DashboardDF$Abstract
Summary  = DashboardDF$Summary
DatasetProcessingSteps = DashboardDF$DatasetProcessingSteps
Comments = DashboardDF$Comments

```
# Abstract

`r Abstract`

# Details

```{r label="Details", echo=FALSE}
data3 <- subset(DashboardDF, select = - c(Abstract,Summary,DatasetProcessingSteps,Comments)) 
kable(t(data3))

```

# Summary

`r Summary`

# Results

## Counts
```{r label="Results-counts", echo=FALSE}

# Get the summarized data for the comp count survey into a data frame
Sql = paste("SELECT
 COW_W_0
, COW_W_1
, COW_W_2
, COW_W_3
, COW
, CALF
, YBULL_SF
, YBULL_GTSF
, SM_BULL
, MED_BULL
, MED_L_BULL
, LG_BULL
, BULL_30_40
, BULL_30_50
, BULL_30_60
, BULL_41_50
, BULL_GT_50
, BULL_GT_60
, BULL_GTE_50
, BULL_LT_30
, BULL_LT_50
, YBULL_ALL
, BULL_ALL
, UNKNOWN
, ADULT
, MOOSE
, N as n
FROM Summary_TotalCountsBySurvey
WHERE (SurveyName = '",SurveyName,"')",sep="")

ResultsDF = GetDataFrame(Sql)
kable(t(ResultsDF))

```

# Metrics

```{r label="Results-metrics", echo=FALSE}
options("digits" = 2)
# Get the summarized data for the comp count survey into a data frame
Sql = paste("SELECT
Area_SqMi
, Area_SqKm
, [Calves: 100 cows]
, [Bulls: 100 cows]
, [Calves: 100 adults]
, [Minimum density (unadjusted moose/sq. mi.)]
, [Area_SqMi, counted]
, [N, counted]
, [N, not counted]
, [N, Counted is NULL]
, [Proportion of units counted]
FROM Summary_TotalCountsBySurvey
WHERE (SurveyName = '",SurveyName,"')",sep="")

ResultsDF = GetDataFrame(Sql)
kable(t(ResultsDF))

```

# Dataset processing steps

`r DatasetProcessingSteps`

# Comments

`r Comments`



